High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-21 notebooks/intro.qmd
references sorted. Now starting writing

measure = 
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, data_name=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

>>>>

measure = 
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, dataname=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```
